High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-09-03 paper/main.tex
minor typo fixes

Studies of the neural code to date have primarily focused on
univariate or multivariate neural patterns~\cite[for review
see][NormEtal06], or (more recently) on patterns of dynamic
first-order correlations~\citep[i.e., interactions between pairs of
brain structures;][]{MannEtal18, FongEtal19}.  We wondered what the
future of this line of work might hold.  For example, is the neural
code mediated by higher-order interactions between brain structures?
Second-order correlations reflect \textit{homologous} patterns of
correlation.  In other words, if the changing patterns of correlations
between two regions, $A$ and $B$, are similar to those between two
other regions, $C$ and $D$, this would be reflected in the
second-order correlations between ($A$--$B$) and ($C$--$D$).  In this
way, second-order correlations identify similarities and differences
between subgraphs of the brain's connectome.  Analogously, third-order
correlations reflect homologies between second-order correlations--
i.e., homologous patterns of homologous interactions between brain
regions.  More generally, higher-order correlations reflect homologies
between patterns of lower-order correlations.  We can then ask: which
``orders'' of interaction are most reflective of high-level cognitive
processes?

>>>>

Studies of the neural code to date have primarily focused on
univariate or multivariate neural patterns~\citep[for review
see][]{NormEtal06}, or (more recently) on patterns of dynamic
first-order correlations~\citep[i.e., interactions between pairs of
brain structures;][]{MannEtal18, FongEtal19}.  We wondered what the
future of this line of work might hold.  For example, is the neural
code mediated by higher-order interactions between brain structures?
Second-order correlations reflect \textit{homologous} patterns of
correlation.  In other words, if the changing patterns of correlations
between two regions, $A$ and $B$, are similar to those between two
other regions, $C$ and $D$, this would be reflected in the
second-order correlations between ($A$--$B$) and ($C$--$D$).  In this
way, second-order correlations identify similarities and differences
between subgraphs of the brain's connectome.  Analogously, third-order
correlations reflect homologies between second-order correlations--
i.e., homologous patterns of homologous interactions between brain
regions.  More generally, higher-order correlations reflect homologies
between patterns of lower-order correlations.  We can then ask: which
``orders'' of interaction are most reflective of high-level cognitive
processes?
